---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
![R-CMD-check](https://github.com/sous20/sparseVector/actions/workflows/R-CMD-check.yaml/badge.svg)(https://github.com/sous20/sparseVector/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# sparseVector

This package provides an S4 class for representing sparse numeric vectors efficiently by storing only non-zero values and their positions. It includes methods for common vector operations including arithmetic, statistical functions, and transformations that maintain sparsity where possible.

## Installation

You can install the development version from GitHub:

``` {r}
# install.packages("devtools")
devtools::install_github("sous20/sparseVector")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sparseVector)
# Create a sparse vector
x <- as(c(1, 0, 0, 4, 0), "sparse_numeric")
y <- as(c(0, 2, 0, 1, 0), "sparse_numeric")
# Perform operations
sparse_add(x, y)
mean(x)
norm(x)
```
