---
title: "Getting Started with sparseVector"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with sparseVector}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
devtools::load_all()
```

## What is sparseVector?

The `sparseVector` package provides an efficient S4 class for representing sparse numeric vectors in R. A sparse vector is one that contains many zeros - instead of storing all elements, we only store the non-zero values and their positions. This saves memory and speeds up computations.

## Basic Usage

### Creating Sparse Vectors

Convert a regular numeric vector to sparse format:
```{r}
library(sparseVector)

# Create a sparse vector from a numeric vector
x <- as(c(1, 0, 0, 4, 0, 2), "sparse_numeric")
x
```

### Arithmetic Operations

Perform element-wise operations:
```{r}
y <- as(c(0, 2, 0, 1, 0, 3), "sparse_numeric")

# Addition
sparse_add(x, y)

# Multiplication
sparse_mult(x, y)

# Subtraction
sparse_sub(x, y)

# Cross product (dot product)
sparse_crossprod(x, y)
```

### Using Operators

You can also use standard R operators:
```{r}
# Addition with +
x + y

# Multiplication with *
x * y

# Subtraction with -
x - y
```

### Statistical Functions

Compute statistics efficiently:
```{r}
# Mean (including zeros)
mean(x)

# L2 Norm
norm(x)

# Standardize
x_std <- standardize(x)
mean(x_std)
```

### Converting Back to Dense Format
```{r}
# Convert sparse to regular numeric vector
as(x, "numeric")
```

## Why Use Sparse Vectors?

- **Memory Efficient**: Store only non-zero values
- **Computation Efficient**: Operations only compute on non-zero elements
- **Easy to Use**: Familiar R interface with + , *, - operators
- **Type Safe**: S4 class with validation
